Interval Probability for Fuzzy Quantum Theories

### 2016-06-21 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add another example...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}

@@

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
we can define a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
by 
\[
\tensor*[_{\mathscr{I}}]{\mu}{}(E)=\iota\left(\tensor*[_{\left[0,1\right]}]{\mu}{}(E)\right)\textrm{ ,}
\]
where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interested properties 
\begin{eqnarray*}
\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
\end{eqnarray*}
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\tensor*[_{\mathscr{I}}]{\mu}{}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}

@@

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
we can define a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
by 
\[
\tensor*[_{\mathscr{I}}]{\mu}{}(E)=\iota\left(\tensor*[_{\left[0,1\right]}]{\mu}{}(E)\right)\textrm{ ,}
\]
where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties 
\begin{eqnarray*}
\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
\end{eqnarray*}
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\tensor*[_{\mathscr{I}}]{\mu}{}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

\begin{example}[One-qubit quantum interval-valued probability measure]
Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
be normalized and written in $\left(\begin{array}{c}
\cos\theta\\
\rme^{\rmi\gamma}\sin\theta
\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
defined by 
\begin{eqnarray*}
\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{1}) & = & \necess\textrm{ ,}\\
\tensor*[_{\mathscr{I}}]{\mu}{}(\proj{\psi}) & = & \begin{cases}
\necess & \textrm{, if }\theta=0\textrm{ ;}\\
\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
\end{cases}
\end{eqnarray*}
Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
as 
\[
\left(\begin{array}{c}
-\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{array}\right)=-\rme^{\rmi\gamma}\left(\begin{array}{c}
\cos\left(\frac{\pi}{2}-\theta\right)\\
\rme^{\rmi\left(\pi-\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
\end{array}\right)
\]
so we have
\[
\tensor*[_{\mathscr{I}}]{\mu}{}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi}\right)\textrm{ .}
\]
Hence, $\tensor*[_{\mathscr{I}}]{\mu}{}$ is a quantum $\mathscr{I}$-interval-valued
probability measure. Notice that for all projection~$E$, $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)\in\tensor*[_{\mathscr{I}}]{\mu}{}(E)$
implies that $\tensor*[_{\mathscr{I}}]{\mu}{}(E)$ is one of quantum
$\mathscr{I}$-interval-valued probability measures corresponding
to $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$. However,
$\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$ can correspond
to infinity many quantum $\mathscr{I}$-interval-valued probability
measures by twisting the definition involving $\gamma$.\qed\end{example}
